Outdated and License-Violating Code on Stack Overflow

### 2017-10-12 cloverflow-tse/cloverflow.tex
Latest update.

\subsection{Phase 2: Clone Merging}
As there are in total 315,786,118 clone pairs reported, it is infeasible for
humans to manually validate them all. Instead of investigating a random sample,
we adopted the idea of \textbf{clone agreement} which has been used in clone
research studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed by
multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we reduced
the number of clone candidates for manual investigation and avoid a threat to
internal validity of double counting the same clone pair twice by merging the
ones agreed by the two tools. To find agreement between two clone pairs
reported by two different tools, we used the clone pair matching metric proposed
by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough
number of overlapping lines can be categorised as either a good-match or an
ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a
confidence value between 0 and 1. Although good-match has stronger
agreement than ok-match, we choose ok-match as our clone merging method because 
it does not take clone size into account which suit our results of clones from
two tools, Simian, SourcererCC, with two different detection methods, 
line-based and method-based.

@@

The work that is closely similar to us is a study by 
An et al.~\cite{An2017} where the authors investigated 
clones between 399 Android apps and Stack Overflow posts. 
They found 1,226 code snippets which were reused from 68 Android apps. 
They also observed that there are 1,279 cases of potential 
license violations. The authors rely on the timestamp to 
judge whether the code has been copied from/to Stack Overflow 
along with confirmations from six developers. Instead of Android apps, 
we investigated clones between Stack Overflow and 111 open 
source projects. Their results are similar to our findings that 
there exist clones from software projects to Stack Overflow with 
potential licensing violations. 
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.

>>>>

\subsection{Phase 2: Clone Merging} As there are in total 315,786,118 clone
pairs reported, it is infeasible for humans to manually validate them all.
Instead of investigating a random sample, we adopted the idea of \textbf{clone
	agreement} which has been used in clone research studies~\cite{Funaro2010,
	Wang2013,cr2016ssbse} in situations where a clone oracle is missing or
impossible to establish. Clone pairs agreed by multiple clone detection tools
have a higher likelihood to be real clones~\cite{cr2016ssbse}. By using this
agreement-based approach, we reduced the number of clone candidates for manual
investigation and avoid a threat to internal validity of double counting the
same clone pair twice by merging the ones agreed by the two tools. To find
agreement between two clone pairs reported by two different tools, we used the
clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two
clone pairs which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as \textit{good}
and \textit{ok} respectively) with a confidence value between 0 and 1. Although
good-match has stronger agreement than ok-match, we choose ok-match as our clone
merging method because it does not take clone size into account. Clone containment suits our
online code clones from two tools, Simian (line-level) and SourcererCC
(method-level), better because Simian's clone fragments  are sometimes smaller or bigger than
a method while SourcererCC's clone fragments are always confined to a method boundary.

@@

The work that is closely similar to us is a study by 
An et al.~\cite{An2017} where the authors investigated 
clones between 399 Android apps and Stack Overflow posts. 
They found 1,226 code snippets which were reused from 68 Android apps. 
They also observed that there are 1,279 cases of potential 
license violations. The authors rely on the timestamp to 
judge whether the code has been copied from/to Stack Overflow 
along with confirmations from six developers. Instead of Android apps, 
we investigated clones between Stack Overflow and 111 open 
source projects. Their results are similar to our findings that 
there exist clones from software projects to Stack Overflow with 
potential licensing violations. 
\FIXME{Add a discussion of Abdalkareem et al.~\cite{Abdalkareem2017}}
%In our work, we defined seven patterns of online code cloning and 
%performed a large-scale manual check of 3,632 clone pairs. 
%We discovered 112 clone pairs with strong evidences, 
%based on natural text in comments and post contents, that they 
%were copied from Qualitas to Stack Overflow. By comparing the 
%clones to their latest versions in the software, we found that 
%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
